**Supplementary Information**

### 2021-04-09 submission/manuscript.tex
Randomly rarefied data bug corrected.

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Seasonal Dynamics of Epiphytic Microbial Communities on Marine Macrophyte Surfaces},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\providecommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{\textbf{Seasonal Dynamics of Epiphytic Microbial Communities on Marine
Macrophyte Surfaces}}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{}
    \preauthor{}\postauthor{}
    \date{}
    \predate{}\postdate{}

\usepackage{times} % Times New Roman font
\usepackage[T1]{fontenc}

@@

@@

Obtained sequences were analysed on the computer cluster Isabella
(University Computing Center, University of Zagreb) using mothur
(version 1.43.0) (Schloss et al., 2009) according to the MiSeq Standard
Operating Procedure (MiSeq SOP; \url{https://mothur.org/wiki/MiSeq_SOP})
(Kozich et al., 2013) and recommendations provided by the Riffomonas
project to enhance data reproducibility
(\url{http://www.riffomonas.org/}). For alignment and classification of
sequences the SILVA SSU Ref NR 99 database (release 138;
\url{http://www.arb-silva.de}) was used (Quast et al., 2013; Yilmaz et
al., 2014). Pipeline data processing and visualization was done using R
(version 3.6.0) (R Core Team, 2019) combined with packages vegan
(version 2.5-6) (Oksanen et al., 2019), tidyverse (version 1.3.0)
(Wickham et al., 2019) and multiple other packages ({\textbf{???}};
Neuwirth, 2014; Xie, 2014, 2015, 2019; Wilke, 2018; Xie et al., 2018;
Allaire et al., 2019; Zhu, 2019). The detailed analysis procedure
including the R Markdown file are available in the GitHub repository
(\url{https://github.com/MicrobesRovinj/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021}).
Based on the ATCC MSA-1002 mock community included in the analysis an
average sequencing error rate of 0.01 \si{\percent} was determined,
which is in line with previously reported values for next-generation
sequencing data (Kozich et al., 2013; Schloss et al., 2016). In
addition, the negative controls processed together with the samples
yielded on average only 2 sequences after sequence quality curation.

@@

Sequencing of the 16S rRNA V4 region yielded a total of 1.8 million
sequences after quality curation and exclusion of sequences without
known relatives (no relative sequences) and eukaryotic, chloroplast and
mitochondrial sequences (\autoref{supp-nseq_notus}). A total of 35
samples originating from epiphytic archaeal and bacterial communities
associated with surfaces of the seagrass \emph{C. nodosa} and the
macroalga \emph{C. cylindracea} were analysed. In addition, 18 samples
(one of the samples was sequenced twice) originating from the ambient
seawater were also processed for comparison. The number of reads per
sample ranged between 8,408 and 77,463 sequences
(\autoref{supp-nseq_notus}). Even when the highest sequencing effort was
applied the rarefaction curves did not level off as commonly observed in
high-throughput 16S rRNA amplicon sequencing approaches
(\autoref{supp-rarefaction}). Following quality curation and exclusion
of sequences as mentioned above reads were clustered into 28,750
different OTUs at a similarity level of 97 \si{\percent}. Read numbers
were normalized to the minimum number of sequences (8,408,
\autoref{supp-nseq_notus}) through rarefaction resulting in 17,025
different OTUs with 347 to 1,977 OTUs per sample
(\autoref{supp-calculators}). To determine seasonal changes in richness
and diversity the observed number of OTUs, Chao1, ACE, Exponential
Shannon and Inverse Simpson (Jost, 2006) were calculated after
normalization through rarefaction. Generally, richness estimators and
diversity indices showed similar trends. On average, higher values were
found for \emph{C. cylindracea} (mixed {[}Number of OTUs, 1,683.5 ±
128.5 OTUs{]} and monospecific {[}Number of OTUs, 1,729.9 ± 145.8
OTUs{]}) than for \emph{C. nodosa} (Number of OTUs, 1,052.2 ± 211.4
OTUs) and lowest values were obtained for the microbial community of the
ambient seawater (Number of OTUs, 529.2 ± 146.8 OTUs)
(\autoref{supp-calculators}). Seasonal changes did not reveal such large
dissimilarities. \emph{C. nodosa} communities showed a slow increase
towards the end of the study, while \emph{C. cylindracea} (mixed and
monospecific) communities were characterized by slightly higher values
in spring and summer than in autumn and winter
(\autoref{supp-calculators}).

To determine the proportion of shared archaeal and bacterial OTUs and
communities sampled in different environments the Jaccard's Similarity
Coefficient on presence-absence data and Bray-Curtis Similarity
Coefficient, respectively, were calculated. Coefficients were determined
after normalization through rarefaction and binning of samples from the
particular environment. The highest proportion of shared OTUs and
community was found between mixed and monospecific \emph{C. cylindracea}
(Jaccard, 0.35; Bray-Curtis, 0.77), while lower shared values were
calculated between ambient seawater and epiphytic communities
(\autoref{matrix}). Shared proportion between \emph{C. nodosa} and
\emph{C. cylindracea} were approximately in-between the values of mixed
and monospecific \emph{C. cylindracea}. To assess seasonal changes in
the proportion of shared OTUs and communities the Jaccard's and
Bray-Curtis Similarity Coefficients were calculated between consecutive
sampling points (\autoref{shared}). Both coefficients showed similar
trends. Temporal proportional changes were more pronounced for ambient
seawater than for \emph{C. nodosa} and especially \emph{C. cylindracea}
associated communities (\autoref{shared}). In addition, only 0.4 -- 1.0
\si{\percent} of OTUs from each surface associated community were
present at all seasons. These persistent OTUs constituted a high
proportion of total sequences (40.2 -- 52.1 \si{\percent}). To further
disentangle the environmental and seasonal community dissimilarity a
Principal Coordinates Analysis (PCoA) based on Bray-Curtis distances and
OTU abundances was applied. A clear separation between ambient seawater
and surface associated communities was found (\autoref{pcoa}). In
addition, a separation of epiphytic bacterial and archaeal communities
based on host species was detected. This separation was further
supported by ANOSIM (R = 0.96, \emph{p} \textless{} 0.001). Seasonal
changes of \emph{C. nodosa} associated communities indicated a
separation between spring, summer and autumn/winter samples (ANOSIM, R =
0.54, \emph{p} \textless{} 0.01). For \emph{C. cylindracea} associated
communities a separation between summer and autumn/winter/spring samples
was observed that was, however, not as strong as for \emph{C. nodosa}
associated communities (ANOSIM, R = 0.30, \emph{p} \textless{} 0.05)
(\autoref{pcoa}).

@@

Sequences classified as \emph{Bacteroidota} comprised, on average, 19.2
± 5.5 \si{\percent} of all sequences (\autoref{bactero}). Similarly to
\emph{Cyanobacteria}, large differences in the taxonomic composition
between ambient seawater and surface associated communities were found
(\autoref{bactero}). The ambient seawater community was characterized by
the NS4 and NS5 marine groups, uncultured \emph{Cryomorphaceae},
uncultured \emph{Flavobacteriaceae}, NS11-12 marine group,
\emph{Balneola}, uncultured \emph{Balneolaceae} and \emph{Formosa}. In
contrast, in surface associated communities \emph{Lewinella},
\emph{Portibacter}, \emph{Rubidimonas}, sequences without known
relatives within the \emph{Saprospiraceae} (no relative
\emph{Saprospiraceae}), uncultured \emph{Saprospiraceae}, (sequences
without known relatives within the \emph{Flavobacteriaceae} (no relative
\emph{Flavobacteriaceae})and uncultured \emph{Rhodothermaceae} were
found. Some groups showed minor seasonal changes such as no relative
\emph{Flavobacteriaceae} whose sequences were more abundant from
November 2017 until June 2018. In contrast, uncultured
\emph{Rhodothermaceae} showed higher proportions from June 2018 until
the end of the study period. Surface associated \emph{Bacteroidota}
communities were very diverse as observed in the high proportion of taxa
clustering as other \emph{Bacteroidota} (\autoref{bactero}).

@@

\emph{Saprospiraceae} (e.g. \emph{Lewinella}, \emph{Portibacter} and

@@

This work was founded by the Croatian Science Foundation through the
MICRO-SEAGRASS project (project number IP-2016-06-7118). ZZ and GJH were
supported by the Austrian Science Fund (FWF) project ARTEMIS (project
number P28781-B21). We would like to thank Margareta Buterer for
technical support, Paolo Paliaga for help during sampling and the
University Computing Center of the University of Zagreb for access to
the computer cluster Isabella.

@@

\leavevmode\hypertarget{ref-Armstrong2000}{}%
Armstrong, E., Rogerson, A., and Leftley, J. (2000). The abundance of
heterotrophic protists associated with intertidal seaweeds.
\emph{Estuar. Coast. Shelf Sci.} 50, 415--424.
doi:\href{https://doi.org/10.1006/ECSS.1999.0577}{10.1006/ECSS.1999.0577}.

@@

\leavevmode\hypertarget{ref-Xie2019a}{}%
Xie, Y. (2019). TinyTeX: A lightweight, cross-platform, and
easy-to-maintain LaTeX distribution based on TeX Live. \emph{TUGboat}
40, 30--32.

@@

{\centering \includegraphics[width=0.7\linewidth]{../results/figures/matrix}

@@

{\centering \includegraphics[width=0.85\linewidth]{../results/figures/seasonal_shared}

@@

{\centering \includegraphics[width=0.55\linewidth]{../results/figures/pcoa_figure}

@@

{\centering \includegraphics[width=0.85\linewidth]{../results/figures/community_bar_plot}

@@

{\centering \includegraphics[width=0.85\linewidth]{../results/figures/cyanobacteria_bar_plot}

@@

{\centering \includegraphics[width=0.85\linewidth]{../results/figures/bacteroidota_bar_plot}

@@

{\centering \includegraphics[width=0.85\linewidth]{../results/figures/alphaproteobacteria_bar_plot}

@@

{\centering \includegraphics[width=0.85\linewidth]{../results/figures/gammaproteobacteria_bar_plot}

@@

{\centering \includegraphics[width=0.85\linewidth]{../results/figures/desulfobacterota_bar_plot}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Seasonal Dynamics of Epiphytic Microbial Communities on Marine Macrophyte Surfaces},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{times} % Times New Roman font
\usepackage[T1]{fontenc}

@@

\title{\textbf{Seasonal Dynamics of Epiphytic Microbial Communities on Marine
Macrophyte Surfaces}}
\author{}
\date{\vspace{-2.5em}}

@@

Obtained sequences were analysed on the computer cluster Isabella
(University Computing Center, University of Zagreb) using mothur
(version 1.43.0) (Schloss et al., 2009) according to the MiSeq Standard
Operating Procedure (MiSeq SOP; \url{https://mothur.org/wiki/MiSeq_SOP})
(Kozich et al., 2013) and recommendations provided by the Riffomonas
project to enhance data reproducibility
(\url{http://www.riffomonas.org/}). For alignment and classification of
sequences the SILVA SSU Ref NR 99 database (release 138;
\url{http://www.arb-silva.de}) was used (Quast et al., 2013; Yilmaz et
al., 2014). Pipeline data processing and visualization was done using R
(version 3.6.0) (R Core Team, 2019) combined with packages vegan
(version 2.5-6) (Oksanen et al., 2019), tidyverse (version 1.3.0)
(Wickham et al., 2019) and multiple other packages (Neuwirth, 2014; Xie,
2014, 2015, 2019a, 2019b; Wilke, 2018; Xie et al., 2018; Allaire et al.,
2019; Zhu, 2019). The detailed analysis procedure including the R
Markdown file are available in the GitHub repository
(\url{https://github.com/MicrobesRovinj/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021}).
Based on the ATCC MSA-1002 mock community included in the analysis an
average sequencing error rate of 0.01 \si{\percent} was determined,
which is in line with previously reported values for next-generation
sequencing data (Kozich et al., 2013; Schloss et al., 2016). In
addition, the negative controls processed together with the samples
yielded on average only 2 sequences after sequence quality curation.

@@

Sequencing of the 16S rRNA V4 region yielded a total of 1.7 million
sequences after quality curation and exclusion of sequences without
known relatives (no relative sequences) and eukaryotic, chloroplast and
mitochondrial sequences (\autoref{supp-nseq_notus}). A total of 35
samples originating from epiphytic archaeal and bacterial communities
associated with surfaces of the seagrass \emph{C. nodosa} and the
macroalga \emph{C. cylindracea} were analysed. In addition, 18 samples
(one of the samples was sequenced twice) originating from the ambient
seawater were also processed for comparison. The number of reads per
sample ranged between 8,408 and 77,463 sequences
(\autoref{supp-nseq_notus}). Even when the highest sequencing effort was
applied the rarefaction curves did not level off as commonly observed in
high-throughput 16S rRNA amplicon sequencing approaches
(\autoref{supp-rarefaction}). Following quality curation and exclusion
of sequences as mentioned above reads were clustered into 28,750
different OTUs at a similarity level of 97 \si{\percent}. Read numbers
were normalized to the minimum number of sequences (8,408,
\autoref{supp-nseq_notus}) through rarefaction resulting in 17,201
different OTUs with 352 to 2,062 OTUs per sample
(\autoref{supp-calculators}). To determine seasonal changes in richness
and diversity the observed number of OTUs, Chao1, ACE, Exponential
Shannon and Inverse Simpson (Jost, 2006) were calculated after
normalization through rarefaction. Generally, richness estimators and
diversity indices showed similar trends. On average, higher values were
found for \emph{C. cylindracea} (mixed {[}Number of OTUs, 1,688.4 ±
136.6 OTUs{]} and monospecific {[}Number of OTUs, 1,750.4 ± 165.7
OTUs{]}) than for \emph{C. nodosa} (Number of OTUs, 1,063.7 ± 210.6
OTUs) and lowest values were obtained for the microbial community of the
ambient seawater (Number of OTUs, 531.0 ± 143.9 OTUs)
(\autoref{supp-calculators}). Seasonal changes did not reveal such large
dissimilarities. \emph{C. nodosa} communities showed a slow increase
towards the end of the study, while \emph{C. cylindracea} (mixed and
monospecific) communities were characterized by slightly higher values
in spring and summer than in autumn and winter
(\autoref{supp-calculators}).

To determine the proportion of shared archaeal and bacterial OTUs and
communities sampled in different environments the Jaccard's Similarity
Coefficient on presence-absence data and Bray-Curtis Similarity
Coefficient, respectively, were calculated. Coefficients were determined
after normalization through rarefaction and binning of samples from the
particular environment. The highest proportion of shared OTUs and
community was found between mixed and monospecific \emph{C. cylindracea}
(Jaccard, 0.35; Bray-Curtis, 0.77), while lower shared values were
calculated between ambient seawater and epiphytic communities
(\autoref{matrix}). Shared proportion between \emph{C. nodosa} and
\emph{C. cylindracea} were approximately in-between the values of mixed
and monospecific \emph{C. cylindracea}. To assess seasonal changes in
the proportion of shared OTUs and communities the Jaccard's and
Bray-Curtis Similarity Coefficients were calculated between consecutive
sampling points (\autoref{shared}). Both coefficients showed similar
trends. Temporal proportional changes were more pronounced for ambient
seawater than for \emph{C. nodosa} and especially \emph{C. cylindracea}
associated communities (\autoref{shared}). In addition, only 0.4 -- 1.0
\si{\percent} of OTUs from each surface associated community were
present at all seasons. These persistent OTUs constituted a high
proportion of total sequences (40.2 -- 53.2 \si{\percent}). To further
disentangle the environmental and seasonal community dissimilarity a
Principal Coordinates Analysis (PCoA) based on Bray-Curtis distances and
OTU abundances was applied. A clear separation between ambient seawater
and surface associated communities was found (\autoref{pcoa}). In
addition, a separation of epiphytic bacterial and archaeal communities
based on host species was detected. This separation was further
supported by ANOSIM (R = 0.96, \emph{p} \textless{} 0.001). Seasonal
changes of \emph{C. nodosa} associated communities indicated a
separation between spring, summer and autumn/winter samples (ANOSIM, R =
0.56, \emph{p} \textless{} 0.01). For \emph{C. cylindracea} associated
communities a separation between summer and autumn/winter/spring samples
was observed that was, however, not as strong as for \emph{C. nodosa}
associated communities (ANOSIM, R = 0.30, \emph{p} \textless{} 0.01)
(\autoref{pcoa}).

@@

Sequences classified as \emph{Bacteroidota} comprised, on average, 19.2
± 5.5 \si{\percent} of all sequences (\autoref{bactero}). Similarly to
\emph{Cyanobacteria}, large differences in the taxonomic composition
between ambient seawater and surface associated communities were found
(\autoref{bactero}). The ambient seawater community was characterized by
the NS4 and NS5 marine groups, uncultured \emph{Cryomorphaceae},
uncultured \emph{Flavobacteriaceae}, NS11-12 marine group,
\emph{Balneola}, uncultured \emph{Balneolaceae} and \emph{Formosa}. In
contrast, in surface associated communities \emph{Lewinella},
\emph{Portibacter}, \emph{Rubidimonas}, sequences without known
relatives within the \emph{Saprospiraceae} (no relative
\emph{Saprospiraceae}), uncultured \emph{Saprospiraceae}, (sequences
without known relatives within the \emph{Flavobacteriaceae} (no relative
\emph{Flavobacteriaceae}) and uncultured \emph{Rhodothermaceae} were
found. Some groups showed minor seasonal changes such as no relative
\emph{Flavobacteriaceae} whose sequences were more abundant from
November 2017 until June 2018. In contrast, uncultured
\emph{Rhodothermaceae} showed higher proportions from June 2018 until
the end of the study period. Surface associated \emph{Bacteroidota}
communities were very diverse as observed in the high proportion of taxa
clustering as other \emph{Bacteroidota} (\autoref{bactero}).

@@

\emph{Saprospiraceae} (e.g.~\emph{Lewinella}, \emph{Portibacter} and

@@

This work was funded by the Croatian Science Foundation through the
MICRO-SEAGRASS project (project number IP-2016-06-7118). ZZ and GJH were
supported by the Austrian Science Fund (FWF) project ARTEMIS (project
number P28781-B21). We would like to thank Margareta Buterer for
technical support, Paolo Paliaga for help during sampling and the
University Computing Center of the University of Zagreb for access to
the computer cluster Isabella.

@@

\leavevmode\hypertarget{ref-Armstrong2000}{}%
Armstrong, E., Rogerson, A., and Leftley, J. W. (2000). The abundance of
heterotrophic protists associated with intertidal seaweeds.
\emph{Estuar. Coast. Shelf Sci.} 50, 415--424.
doi:\href{https://doi.org/10.1006/ECSS.1999.0577}{10.1006/ECSS.1999.0577}.

@@

\leavevmode\hypertarget{ref-Xie2019a}{}%
Xie, Y. (2019a). TinyTeX: A lightweight, cross-platform, and
easy-to-maintain LaTeX distribution based on TeX Live. \emph{TUGboat}
40, 30--32.

\leavevmode\hypertarget{ref-Xie2019b}{}%
Xie, Y. (2019b). \emph{tinytex: Helper functions to install and maintain
'TeX Live', and compile 'LaTeX' documents}.

@@

{\centering \includegraphics[width=0.7\linewidth]{/mydisk/POSAO2/isabella/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021/results/figures/matrix}

@@

{\centering \includegraphics[width=0.85\linewidth]{/mydisk/POSAO2/isabella/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021/results/figures/seasonal_shared}

@@

{\centering \includegraphics[width=0.55\linewidth]{/mydisk/POSAO2/isabella/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021/results/figures/pcoa_figure}

@@

{\centering \includegraphics[width=0.85\linewidth]{/mydisk/POSAO2/isabella/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021/results/figures/community_bar_plot}

@@

{\centering \includegraphics[width=0.85\linewidth]{/mydisk/POSAO2/isabella/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021/results/figures/cyanobacteria_bar_plot}

@@

{\centering \includegraphics[width=0.85\linewidth]{/mydisk/POSAO2/isabella/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021/results/figures/bacteroidota_bar_plot}

@@

{\centering \includegraphics[width=0.85\linewidth]{/mydisk/POSAO2/isabella/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021/results/figures/alphaproteobacteria_bar_plot}

@@

{\centering \includegraphics[width=0.85\linewidth]{/mydisk/POSAO2/isabella/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021/results/figures/gammaproteobacteria_bar_plot}

@@

{\centering \includegraphics[width=0.85\linewidth]{/mydisk/POSAO2/isabella/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021/results/figures/desulfobacterota_bar_plot}

### 2021-04-09 submission/supplementary.Rmd
Coauthors review done.
Randomly rarefied data bug corrected.

\linenumbers
\sisetup{mode=text}
\setlength\parindent{24pt}

@@

```{r out.width="85%", fig.align="center", fig.cap="Rarefaction curves of bacterial and archaeal communities from the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater.\\label{rarefaction}", fig.pos="H"}
include_graphics("../results/figures/rarefaction.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Seasonal dynamics of observed number of OTUs, Chao1, ACE, exponential of the Shannon diversity index and Inverse Simpson index of bacterial and archaeal communities from the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater.\\label{calculators}", fig.pos="H"}
include_graphics("../results/figures/calculators.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Relative contribution of chloroplast sequences on the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater.\\label{chloroplast}", fig.pos="H"}
include_graphics("../results/figures/chloroplast_bar_plot.jpg")
```

>>>>

[]: # (\linenumbers)
\sisetup{mode=text}
\setlength\parindent{24pt}

@@

```{r out.width="85%", fig.align="center", fig.cap="Rarefaction curves of bacterial and archaeal communities from the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater.\\label{rarefaction}", fig.pos="H"}
include_graphics(normalizePath("results/figures/rarefaction.jpg"))
```

```{r out.width="85%", fig.align="center", fig.cap="Seasonal dynamics of observed number of OTUs, Chao1, ACE, exponential of the Shannon diversity index and Inverse Simpson index of bacterial and archaeal communities from the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater.\\label{calculators}", fig.pos="H"}
include_graphics(normalizePath("results/figures/calculators.jpg"))
```

```{r out.width="85%", fig.align="center", fig.cap="Relative contribution of chloroplast sequences on the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater.\\label{chloroplast}", fig.pos="H"}
include_graphics(normalizePath("results/figures/chloroplast_bar_plot.jpg"))
```
